Arrows for Parallel Computations

### 2017-10-17 paper/content/arrows.tex
Enquotes

\subsection{Arrows}
\label{sec:arrows}
Arrows were introduced by \citet{HughesArrows} as a general interface for computation. An Arrow |arr a b| represents  a computation that converts an input |a| to an output |b|. This is defined in the |Arrow| type class shown in Fig.~\ref{fig:ArrowDefinition}.
%
To lift an ordinary function to an Arrow, |arr| is used, analogous to the monadic |return|. Similarly, the composition operator |>>>| is analogous to the monadic composition |>>=| and combines two arrows |arr a b| and |arr b c| by "wiring" the outputs of the first to the inputs to the second to get a new arrow |arr a c|. Lastly, the |first| operator takes the input Arrow |arr a b| and converts it into an arrow on pairs |arr (a, c) (b, c)| that leaves the second argument untouched. It allows us to to save input across arrows. Figure~\ref{fig:arrows-viz} shows a graphical representation of these basic Arrow combinators.
The most prominent instances of this interface are regular functions |(->)|
and the Kleisli type (Fig.~\ref{fig:ArrowDefinition}), which wraps monadic functions, e.g.  |a -> m b| (with |m| being a Monad).

>>>>

\subsection{Arrows}
\label{sec:arrows}
Arrows were introduced by \citet{HughesArrows} as a general interface for computation. An Arrow |arr a b| represents  a computation that converts an input |a| to an output |b|. This is defined in the |Arrow| type class shown in Fig.~\ref{fig:ArrowDefinition}.
%
To lift an ordinary function to an Arrow, |arr| is used, analogous to the monadic |return|. Similarly, the composition operator |>>>| is analogous to the monadic composition |>>=| and combines two arrows |arr a b| and |arr b c| by \enquote{wiring} the outputs of the first to the inputs to the second to get a new arrow |arr a c|. Lastly, the |first| operator takes the input Arrow |arr a b| and converts it into an arrow on pairs |arr (a, c) (b, c)| that leaves the second argument untouched. It allows us to to save input across arrows. Figure~\ref{fig:arrows-viz} shows a graphical representation of these basic Arrow combinators.
The most prominent instances of this interface are regular functions |(->)|
and the Kleisli type (Fig.~\ref{fig:ArrowDefinition}), which wraps monadic functions, e.g.  |a -> m b| (with |m| being a Monad).

### 2017-10-17 paper/content/parallelHaskells.tex
Enquotes

There exist several parallel Haskells already. Among the most important are probably GpH  (based on |par| \& |pseq| "hints") \cite{Trinder1996,Trinder1998a}, the |Par| Monad (a monad for deterministic parallelism) \cite{par-monad,Foltzer:2012:MPC:2398856.2364562}, Eden (a parallel Haskell for distributed memory) \cite{eden,Loogen2012}, HdpH (a Template Haskell based parallel Haskell for distributed memory) \cite{Maier:2014:HDS:2775050.2633363,stewart_maier_trinder_2016} and LVish (a |Par| extension with focus on communication) \cite{Kuper:2014:TPE:2666356.2594312}.

>>>>

There exist several parallel Haskells already. Among the most important are probably GpH  (based on |par| \& |pseq| \enquote{hints}) \cite{Trinder1996,Trinder1998a}, the |Par| Monad (a monad for deterministic parallelism) \cite{par-monad,Foltzer:2012:MPC:2398856.2364562}, Eden (a parallel Haskell for distributed memory) \cite{eden,Loogen2012}, HdpH (a Template Haskell based parallel Haskell for distributed memory) \cite{Maier:2014:HDS:2775050.2633363,stewart_maier_trinder_2016} and LVish (a |Par| extension with focus on communication) \cite{Kuper:2014:TPE:2666356.2594312}.
